Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)

### 2025-01-15 paper/paper.qmd
more changes

---
title: "Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| warning: false
#| message: false
summary(hansard_corpus)

@@

```{r}
#| warning: false
#| message: false
# Review entries where questions or answers are marked
question_instances <- hansard_corpus %>%
  filter(question == 1)
print(question_instances)
```

@@

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
git config --global http.postBuffer 524288000

git config --global http.postBuffer 629145600

git reset --soft HEAD~1

git lfs install
git lfs track "*.parquet"
git add .gitattributes
git commit -m "Track large parquet files with Git LFS"
git add data/01-raw_data/hansard-corpus/hansard_corpus_1998_to_2022.parquet
git commit -m "Add large Hansard Parquet file"
git push origin main

@@

# Results

>>>>

---
title: "Silenced in the Chamber: Analyzing Gendered Speech Interruptions in the Australian Parliament (1998–2022)"
author: 
  - Hannah Yu
  - Rohan Alexander
thanks: "Code and data are available at: https://github.com/hannahyu07/Hansard_Interruptions"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| include: false
#| warning: false
#| message: false
summary(hansard_corpus)

@@

```{r}
#| include: false
#| warning: false
#| message: false
# Review entries where questions or answers are marked
question_instances <- hansard_corpus %>%
  filter(question == 1)
print(question_instances)
```

@@

@@
